\clearpage

\begin{center}
    \textbf{\Large Acknowledgement}
\end{center}

\vspace{1cm}
\onehalfspacing
\noindent

I would like to express my sincere gratitude to every individual whose support and guidance have been invaluable throughout the completion of this thesis.

First and foremost, I am deeply grateful to my supervisor, Dr. Dhanajay Kumar Tiwari, for his unwavering support, insightful guidance, and constant encouragement. His expertise and feedback have been crucial in shaping this thesis.

I am also thankful to my friends Keshav, Siddharth, Sandeep, Chetna, Dharm, and many others, whose support, discussions, and encouragement have been immensely helpful throughout this journey. Their assistance and companionship have made this challenging process more manageable and enjoyable.

I would also like to extend my gratitude to all the faculty members of the Department of Linguistics, for their support, feedback, and suggestions.

A special mention goes to the late William John Hutchins, whose pioneering work and extensive research in the field of machine translation have been a cornerstone for my thesis. His compilations and summaries on the development of machine translation since its inception have provided a substantial foundation and inspiration for my research.

Finally, I would like to thank my family for their continuous support and understanding during my studies. Their belief in me has been a driving force in my academic pursuits.

Thank you all for your invaluable support.

\vspace{2cm}
\rightline{Bhanu Pratap Singh}
\rightline{2019IMSLI003}
\doublespacing

\clearpage